State of the Practice for Medical Imaging Software

### 2022-07-12 StateOfPractice/Papers/MedImageSoft_SOP-arXiv/MedImageSoft_SOP_AcademicRadiology.tex
Edits to introduction to pain points section

Based on interviews with nine developers (described in
Section~\ref{sec_interview_methods}), we answer three research questions:
\rqref{RQ_PainPoints}) What are the pain points for developers working on
research software projects?; \rqref{RQ_ComparePainPoints}) How do the pain
points of developers from MI compare to the pain points for research software in
general?; and \rqref{RQ_Concerns}) For MI developers what specific best practices
are taken to address the pain points and software quality concerns?  We go
through each of the identified pain points and include citations that contrast
the MI experience with observations from researchers in other domains.  We also
cover potential ways to address the pain points, as promoted by the community in
this section, and based on our experience in Section~\ref{ch_recommendations}.

Ways to address pain points found by community as part of the qualitative data
from developer interviews (Section~\ref{sec_interview_methods}).  The practices
we summarize can potentially be emulated by the MI software packages that do not
currently follow them.  Moreover, these practices may also provide examples that
can be followed by other research software domains.

\begin{itemize}
\item Hard to have a high level roadmap from the start
\item Not enough participants for usability tests
\item Only a few people fully understand the large codebase
\item Hard to transfer to new technologies
\item Hard to understand users' needs
\item Hard to maintain good documentations
\end{itemize}

\citet{PintoEtAl2018} lists some pain points that did not come up in our
conversations with LBM developers: Cross-platform compatibility, interruptions
while coding, scope bloat, lack of user feedback, hard to collaborate on
software projects, and aloneness. \citet{WieseEtAl2019} repeat some of the
previous pain points and add the following: dependency management, data handling
concerns (like data quality, data management and data privacy), reproducibility,
and software scope determination. Although LBM developers did not mention these
pain points, we cannot conclude that they are not relevant for LBM software
development, since we only interviewed four LBM developers for about an hour each.

@@

\item[P\refstepcounter{pnum}\thepnum \label{P_LackDevTime}:] \textbf{Lack of
Development Time:} A developer of pyLBM noted that their small development team
has a lack of time to implement new features. Small development teams are common
for LBM software packages (as shown in the measurement table excerpt in
Figure~\ref{measurement_template_image}). Other domains of research software
also experience the lack of time pain point \citep{PintoEtAl2018, PintoEtAl2016,
WieseEtAl2019}. Developers identified a resource related pain point caused by a
lack of funding and time.  Potential and proven solutions suggested by the
interviewees include:

@@

@@

@@

>>>>

Based on interviews with nine developers (described in
Section~\ref{sec_interview_methods}), we answer three research questions:
\rqref{RQ_PainPoints}) What are the pain points for developers working on
research software projects?; \rqref{RQ_ComparePainPoints}) How do the pain
points of developers from MI compare to the pain points for research software in
general?; and \rqref{RQ_Concerns}) For MI developers what specific best
practices are taken to address the pain points and software quality concerns?
The identified pain points relate to lack of time and funding, technology
hurdles, improving correctness, and improving usability.  We go through each
pain points and include citations that contrast the MI experience with
observations from other domains.  We also cover potential ways to address the
pain points, as promoted by the community in this section, and based on our
experience in Section~\ref{ch_recommendations}.  In this section we also discuss
some MI developer strategies for improving maintainability and reproducibility.
These two qualities were not explicitly idenfied as pain points, but ways to
improve them were still part of our interview discussions. The MI interviewee
practices to address pain points and improve quality can potentially be emulated
by other the MI software packages.  Moreover, these practices may provide
examples that can be followed by other research software domains.

\citet{PintoEtAl2018} lists some pain points that did not come up in our
conversations with LBM developers [CHECK  THESE]: Cross-platform compatibility, interruptions
while coding, scope bloat, lack of user feedback, hard to collaborate on
software projects, and aloneness. \citet{WieseEtAl2019} repeat some of the
previous pain points and add the following: dependency management, data handling
concerns (like data quality, data management and data privacy), reproducibility,
and software scope determination. Although LBM developers did not mention these
pain points, we cannot conclude that they are not relevant for LBM software
development, since we only interviewed four LBM developers for about an hour each.

@@

\item[P\refstepcounter{pnum}\thepnum \label{P_LackDevTime}:] \textbf{Lack of
Development Time:} A developer of pyLBM noted that their small development team
has a lack of time to implement new features. Small development teams are common
for LBM software packages (as shown in the measurement table excerpt in
Figure~\ref{measurement_template_image}). Other domains of research software
also experience the lack of time pain point \citep{PintoEtAl2018, PintoEtAl2016,
WieseEtAl2019}. Developers identified a resource related pain point caused by a
lack of funding and time.

Potential and proven solutions suggested by the
interviewees include:

@@

% Hard to transfer to new technologies %from Ao

@@

% Hard to maintain good documentations % from Ao
% \begin{itemize}
%     \item Hard to have a high level roadmap from the start
%     \item Only a few people fully understand the large codebase
% \end{itemize}

@@

%\item Not enough participants for usability tests %from Ao
%Hard to understand users' needs % from Ao
